Evaluation of Types

### 2020-05-16 evaluation/R/evaluate-type-analysis.Rmd
Increase label size
stuff

```{r high-level, echo=FALSE, eval=TRUE}
total_package_count <- nrow(distinct(type_analysis_data, package_name))
total_function_count <- nrow(distinct(type_analysis_data, package_name, function_name))
```

>>>>

Make S3-less data frame, too.

```{r}
S3_funs <- read_csv("../data/package-functions.csv") %>% select(package, fun, is_s3_dispatch, is_s3_method) %>% filter(is_s3_method | is_s3_method) %>% select(package, fun)

S3_funs <- S3_funs %>% rename("package_name" = "package", "function_name" = "fun")

type_analysis_data_no_S3 <- type_analysis_data %>% anti_join(S3_funs)
```

```{r high-level, echo=FALSE, eval=TRUE}
total_package_count <- nrow(distinct(type_analysis_data, package_name))
total_function_count <- nrow(distinct(type_analysis_data, package_name, function_name))

total_package_count_no_S3 <- nrow(distinct(type_analysis_data_no_S3, package_name))
total_function_count_no_S3 <- nrow(distinct(type_analysis_data_no_S3, package_name, function_name))
```
